Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

### 2024-03-02 docs/_tex/index.tex
add disc

The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
shows that the 531 nm band is the most important spectral band for
accurately identifying Chlorophyceae. In fact, at this wavelength,
Chlorophyceae exhibits the highest reflectance among all other classes,
highlighting the difference in accessories carotenoid proportion between
seagrasses and green algae (\citep{repolho2017seagrass}).

@@

\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
both low-altitude and high-altitude flights over a common area. The red
dashed line represents a 1 to 1 relationship.}

@@

In the present study, the main novelty is the usage of two different
altitude (12m and 120m) in the neural network model building. The
spatial resolution of the low altitude fights (8mm) allows for an
accurate selection of pure pixel of the classes used in the neural
network model

>>>>

The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
shows that the 531 nm band is the most important spectral band for
accurately identifying Chlorophyceae. In fact, at this wavelength,
Chlorophyceae exhibits the highest reflectance among all other classes,
highlighting the difference in accessories carotenoid proportion between
seagrasses and green algae \citep{repolho2017seagrass}.

@@

\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
both low-altitude and high-altitude flights over a common area. The red
dashed line represents a linear model wheras the black dashed line
represents a 1 to 1 relationship.}

@@

In this study, a key innovation lies in the utilization of two different
altitudes (12m and 120m) for constructing the neural network model. The
lower altitude flights (8mm spatial resolution) enable precise selection
of pure pixels representing the classes used in the neural network
model. This methodology implies a consistency between the reflectance of
both altitude.

Figure~\ref{fig-CompareRef} depicts the relationship between reflectance
from a low-altitude flight and a high-altitude flight conducted over the
same area. An apparent underestimation of reflectance values is observed
in the high-altitude flight, particularly for higher values. Since both
flights were conducted over vegetation areas, the highest reflectance
values correspond to the infrared part of the spectrum. The disparity in
infrared reflectance may stem from temporal differences between the
flights, possibly resulting in a slightly drier intertidal area and
consequently higher infrared reflectance. This disparity poses an issue
for the methodology followed in the present study, relying solely on one
flight height for training. To address this issue, we employed min/max
standardized reflectance spectra as predictors for the model
(Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us to
eliminate differences in the level of reflectance, focusing instead on
the shape of the spectra. This is a key feature in building a model that
can reliably predict vegetation across geographical sites and seasons.
It enables consistent prediction of vegetation classes across variations
in biomass and variability in light conditions \citetext{\citealp[
]{fyfe2003spatial}; \citealp[
]{COSTA2021107018}; \citealp{piaser2023impact}}.

### 2024-03-02 index.qmd
add disc

The VIP analysis of the Neural Network model (@fig-VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae (@repolho2017seagrass).

@@

plot <- df %>% 
  group_by(pred) %>% 
  sample_n(10000) %>%
  mutate(Low = Low /10000, 
         High = High/10000) %>% 
  ggplot(aes(x=Low, y=High))+
  # geom_point(aes(color = as.factor(pred)))
  ggpointdensity::geom_pointdensity(adjust = .03)+
  viridis::scale_color_viridis(limits = c(0,6000),
                               breaks = c(0,2000,4000,6000),
                               labels = c("1","2000","4000","6000"))+
  # geom_smooth(method = "loess")+
  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "red" )+
  theme_Bede()+
  ylim(c(0.05,0.6))+
  xlim(c(0.05,0.6))+
  ylab("Reflectance of the 120m flight")+
  xlab("Reflectance of the 12m flight")+
  labs(color = "Pixel density")+
  theme(
    legend.position = "top",
        legend.key.width = unit(3,"line"))

ggsave("./Figures/Compare_reflectance.png",plot, width= 472*4, height=402*4, units = "px")

@@

::: columns
::: column
```{r Plot Reflectance_Validation 2 height}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a 1 to 1 relationship. 
#| label: fig-CompareRef
#| fig-width: 5
#| fig-height: 5
#| out-width: "50%"

@@

::: column
In the present study, the main novelty is the usage of two different altitude (12m and 120m) in the neural network model building. The spatial resolution of the low altitude fights (8mm) allows for an accurate selection of pure pixel of the classes used in the neural network model
:::
:::

>>>>

The VIP analysis of the Neural Network model (@fig-VIP) shows that the 531 nm band is the most important spectral band for accurately identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae exhibits the highest reflectance among all other classes, highlighting the difference in accessories carotenoid proportion between seagrasses and green algae [@repolho2017seagrass].

@@

plot <- df %>% 
  group_by(pred) %>% 
  sample_n(10000) %>% 
  mutate(Low = Low /10000, 
         High = High/10000) %>% 
  ggplot(aes(x=Low, y=High))+
  # geom_point(aes(color = as.factor(pred)))
  ggpointdensity::geom_pointdensity(adjust = .03)+
  viridis::scale_color_viridis(limits = c(0,6000),
                               breaks = c(0,2000,4000,6000),
                               labels = c("1","2000","4000","6000"))+
  # geom_smooth(method = "loess")+
  geom_abline(intercept = 0, slope = 1, linewidth = 1, linetype = "dashed", color = "black" )+
  geom_smooth(method = "lm", color = "red", linetype = "dashed",linewidth = 1)+
  theme_Bede()+
  ylim(c(0.05,0.6))+
  xlim(c(0.05,0.6))+
  ylab("Reflectance of the 120m flight")+
  xlab("Reflectance of the 12m flight")+
  labs(color = "Pixel density")+
  theme(
    legend.position = "top",
        legend.key.width = unit(3,"line"))
plot
ggsave("./Figures/Compare_reflectance.png",plot, width= 472*4, height=402*4, units = "px")

@@

::: columns
::: column
```{r Plot Reflectance_Validation 2 height}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship. 
#| label: fig-CompareRef
#| fig-width: 5
#| fig-height: 5
#| out-width: "50%"

@@

::: column
In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model. The lower altitude flights (8mm spatial resolution) enable precise selection of pure pixels representing the classes used in the neural network model. This methodology implies a consistency between the reflectance of both altitude.
:::
:::

 @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area. An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values. Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum. The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance. This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training. To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]). This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra. This is a key feature in building a model that can reliably predict vegetation across geographical sites and seasons. It enables consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
